---
title: ""
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
---

```{r setup, include=FALSE}
## Global options
knitr::opts_chunk$set(cache = TRUE)
```

# **Challenge**

```{r library}
library(tidyverse)
library(here)
```

```{r data_read}
hiphop <- read_csv(here("Data","hiphop.csv"))
head(hiphop)
```

```{r data_clean}
hiphop1 <- hiphop %>%
  mutate(numOverallArtists = replace(numOverallArtists, is.na(numOverallArtists), 0)) %>%
  mutate(numPreferredArtists = replace(numPreferredArtists, is.na(numPreferredArtists), 0)) %>%
  mutate(sex = factor(sex), ethnic = factor(ethnic))

# Since NA data was more than half the observations, instead of dropping the NA's they were converted to 0's
```

Use the dataset to suggest a track listing (11 song titles) for Aubrey's next album with the Biebs. Explain your thought process and corresponding code.

```{r track_listing}
track_listing <- hiphop1 %>%
  mutate(county1 = cut(county, breaks = c(0,99905,331582,3053793), labels=c('Small', 'Medium', 'Large'))) %>%
  select(hiphop, bieber, county1, word, familiarity) %>%
  filter(county1 == 'Large',
         bieber >= quantile(bieber, 0.5),
         hiphop >= 3) %>% 
  group_by(word) %>%
  summarize(population_appeal = mean(familiarity)) %>%
  slice_max(order_by = population_appeal, n =12)

track_listing

```

Song Titles:

1.  Feel me

2.  I'm off the hook

3.  Hella Guap

4.  Make it rain

5.  What it do babe?

6.  Finna stay

7.  Ashy Elbows

8.  My boo

9.  Ballin out

10. What it is, What it was!

11. Player Hater

These titles were specifically chosen for the track list as the words in the titles are recognizable to authentic hip hop fans (hiphop \>=3). Moreover, due to the collaboration with Bieber, the target population is Bieber fans with a high interest in hip hop (quantile(bieber, 0.5)). Finally, the county has been set to 'Large' to target high population areas.
