---
title: "Lab2_Arora"
date: "2022-10-03"
output:
  rmdformats::readthedown:
    highlight: kate
---

```{r setup, include=FALSE}
## Global options
knitr::opts_chunk$set(cache = TRUE)
```

# **Lab 2: HipHop Lyrics**

```{r library}
library(tidyverse)
library(ggplot2)
library(here)
```

```{r data_read}
hiphop <- read_csv(here("Data","hiphop.csv"))
head(hiphop)
```

**The Dataset**

The data set "hiphop" contains results from a study conducted by a
linguist at the University of Minnesota. The researcher was interested
in predicting musical taste based on familiarity with African American
English (AAE). 168 subjects participated in the study, and each was
asked to define 64 different AAE terms. The definitions given were used
to create a "familiarity" score for each subject for each term. This
score quantifies how well the subject knew the term on a scale of 1-5 (1
= not at all, 5 = very well). Before tackling the problems, study the
information on the following website, which includes a description of
each variable:

<http://conservancy.umn.edu/bitstream/handle/11299/116327/5/explanationAAEHiphopChesley.txt>

**Assignment**

[Summary]{.underline}

1.  Provide a brief overview (2-4 sentences) of the dataset. (It is
    always good practice to start an analysis by getting a feel for the
    data and providing a quick summary for readers.) You do not need to
    show any source code for this question, although you probably want
    to use code to get information.

The dataset, 'HipHop' contains survey data for 168 participants (51
males and 117 females). Each participant defined 64 different AAE terms
which were used to create the response variable, 'familiarity'. The
dataset consists of 10752 observations and 38 total variables which
include demographic variables, social network variables, music
variables, pop-cultural variables, artist variables and experimental
items. The maximum and minimum age among the participants was 48 and 16
respectively.

2.  Clean the dataset in whichever ways you see fit. This might mean
    adjusting variable type, for example from "character" to "factor",
    or dealing with missing data.

```{r data_clean}
hiphop1 <- hiphop %>%
  mutate(numOverallArtists = replace(numOverallArtists, is.na(numOverallArtists), 0)) %>%
  mutate(numPreferredArtists = replace(numPreferredArtists, is.na(numPreferredArtists), 0)) %>%
  mutate(sex = factor(sex), ethnic = factor(ethnic))

# Since NA data was more than half the observations, instead of dropping the NA's they were converted to 0's

```

3.  How many unique AAVE words were studied in this dataset?

```{r unique_words}
length(unique(hiphop$word))
```

4.  Make a new variable that recategorizes ethnic into only two groups,
    "white" and "non-white", to simplify your data.

```{r ethnicity}
hiphop1 <- hiphop1 %>%
  mutate(ethnicity =ifelse(ethnic=="white","white","non-white")) %>%
  mutate(ethnicity = factor(ethnicity))
```

5.  What are the demographics of the people in this study? Investigate
    the variables sex, age, and ethnic and summarize your findings in
    1-3 complete sentences.

```{r demographics}
hiphop_dem <- hiphop1 %>%
  select(sex, subj, age, ethnicity)

hiphop_dem_1 <- unique(hiphop_dem)
summary(hiphop_dem_1)
```

The demographics of the dataset show that there are less males (57) than females (117). Also, there are more white people taking the survey (135) than non-white people. Moreover, the range of the ages of people taking the survey is 32 (48-16), with the IQR being 2 (20-18).

6.  Make at least two plots to display the demographic information of
    the subjects in this study. You do not need to discuss these plots,
    but make sure they are appropriate to the data types and have
    informative titles and axis labels.

```{r plots1}
hiphop1 %>%
  ggplot(aes(x= age, y= ethnicity, fill=sex)) +
  geom_boxplot() +
  labs(title = "Distribution of Participants with Respect to Age, Ethnicity and Sex")

```

```{r plots2}
hiphop1 %>%
  ggplot(aes(x= age, fill=ethnicity)) +
  geom_histogram(position = "dodge") +
  labs(title = "Distribution of Participants with Respect to Age and Ethnicity")
```

**Familiar words**

1.  For each demographic group listed below, determine which word(s) in
    this study was the most and least familiar on average.

-   People below the age of 20

```{r words}
familiar_words <- hiphop1 %>%
  filter(age < 20) %>%
  group_by(word) %>%
  summarize(mean_familiarity = mean(familiarity))

familiar_words %>%
  slice_max(mean_familiarity,n =1)

familiar_words %>%
  slice_min(mean_familiarity,n=1)
```

Most Popular Word (age < 20): off the hook

Least Popular Word (age < 20): catch the vapors

-   Non-white women

```{r words1}
familiar_words_1 <- hiphop1 %>%
  filter(sex == "Female", ethnicity == "non-white") %>%
  group_by(word) %>%
  summarize(mean_familiarity_1 = mean(familiarity))

familiar_words_1 %>%
  slice_max(mean_familiarity_1,n =1)

familiar_words_1 %>%
  slice_min(mean_familiarity_1,n=1)
```

Most Popular Word (sex='Female', ethnicity='non-white'): feel me

Least Popular Words (sex='Female', ethnicity='non-white'): break someone out, dukey rope, plex and rollie

-   White men above the age of 30

```{r words2}
familiar_words_2 <- hiphop1 %>%
  filter(sex == "Male", ethnicity == "white", age > 30) %>%
  group_by(word) %>%
  summarize(mean_familiarity_2 = mean(familiarity))

familiar_words_2 %>%
  slice_max(mean_familiarity_2,n =1)

LM <- familiar_words_2 %>%
  slice_min(mean_familiarity_2,n=1)
LM
```

Most Popular Word (sex='Male', ethnicity='white', age > 30): 5-0

Least Popular Words (sex='Male', ethnicity='white', age > 30): see variable LM

2.  For each demographic comparison below, determine which music genre
    most differentiates the groups. That is, which genre had much higher
    average (mean or median) score in one group than the other.

-   Male versus Female

```{r genre}
hiphop1 %>%
  distinct(subj, sex, intl, vocal, classical, folk, rock, country, pop, alternative, hiphop, unclassifiable) %>%
  group_by(sex) %>%
  summarize(mean_intl = mean(intl), mean_vocal = mean(vocal), mean_classical = mean(classical), mean_folk = mean(folk), mean_rock = mean(rock), mean_country = mean(country), mean_pop = mean(pop), mean_alternative = mean(alternative), mean_hiphop = mean(hiphop), mean_unclassifiable = mean(unclassifiable)) %>%
  pivot_longer(mean_intl:mean_unclassifiable, names_to = 'Genre', values_to = 'Mean_Genre') %>%
  pivot_wider(names_from = sex, values_from = Mean_Genre) %>%
  mutate(Diff = abs(Female-Male)) %>%
  arrange(desc(Diff))
```

Rock differentiates the most between Males and Females

-   White versus Non-White

```{r genre1}
hiphop1 %>%
  group_by(ethnicity) %>%
  distinct(subj, sex, intl, vocal, classical, folk, rock, country, pop, alternative, hiphop, unclassifiable) %>%
  summarize(mean_intl = mean(intl), mean_vocal = mean(vocal), mean_classical = mean(classical), mean_folk = mean(folk), mean_rock = mean(rock), mean_country = mean(country), mean_pop = mean(pop), mean_alternative = mean(alternative), mean_hiphop = mean(hiphop), mean_unclassifiable = mean(unclassifiable)) %>%
  pivot_longer(mean_intl:mean_unclassifiable, names_to = 'Genre', values_to = 'Mean_Genre') %>%
  pivot_wider(names_from = ethnicity, values_from = Mean_Genre) %>%
  mutate(Diff = abs(white-`non-white`)) %>%
  arrange(desc(Diff))
```

Intl differentiates the most between White and Non-White

-   Age below 21 versus age 21+

```{r genre2}
hiphop1 <- hiphop1 %>%
  mutate(age1 =ifelse(age < 21,"Below 21","Above 21")) %>%
  mutate(age1 = factor(age1))

hiphop1 %>%
  group_by(age1) %>%
  distinct(subj, sex, intl, vocal, classical, folk, rock, country, pop, alternative, hiphop, unclassifiable) %>%
  summarize(mean_intl = mean(intl), mean_vocal = mean(vocal), mean_classical = mean(classical), mean_folk = mean(folk), mean_rock = mean(rock), mean_country = mean(country), mean_pop = mean(pop), mean_alternative = mean(alternative), mean_hiphop = mean(hiphop), mean_unclassifiable = mean(unclassifiable)) %>%
  pivot_longer(mean_intl:mean_unclassifiable, names_to = 'Genre', values_to = 'Mean_Genre') %>%
  pivot_wider(names_from = age1, values_from = Mean_Genre) %>%
  mutate(Diff = abs(`Above 21`-`Below 21`)) %>%
  arrange(desc(Diff))
```

Alternative differentiates the most between Ages above and below 21

**Use the data**

A former Canadian child TV star named Aubrey Graham is interested in
switching careers to become a rapper. Aubrey hires you to consult the
hiphop dataset to help compose his new songs.

Note: There is no single right answer to these questions. You will need
to think about how you want to address the question, and do the
appropriate variable adjustments and calculations to come up with a
reasonable answer.

1.  Aubrey hopes that his songs will be perceived as authentically
    hiphop. He hopes his lyrics will be recognizeable to those who
    describe themselves as hiphop fans, but less recognizeable to those
    who do not consider themselves fans. Suggest some words or phrases
    that Aubrey should try to use, and some words he should avoid.

```{r aubrey}
fans <- hiphop1 %>%
 distinct(subj, hiphop, word, familiarity) %>%
  filter(hiphop >= quantile(hiphop,0.90)) %>%
  group_by(word) %>%
  summarise(mean_familiarity_3 = mean(familiarity)) %>%
  slice_max(mean_familiarity_3, n = 10)
  

nonfans <- hiphop1 %>%
  distinct(subj, hiphop, word, familiarity) %>%
  filter(hiphop <= quantile(hiphop,0.10)) %>%
  group_by(word) %>%
  summarise(mean_familiarity_3 = mean(familiarity)) %>%
  slice_max(mean_familiarity_3, n = 10)

nonfans

anti_join(fans, nonfans, by = "word")
```

Words to choose: finna, what it is?, 5-0

Words to avoid: off the hook, feel me, boo

2.  Although Aubrey wants to be authentic, he also hopes to sell
    records, of course. Two titles have been suggested for his first
    album: "Hotline Boo" or "Hella Bling". Based on the dataset, which
    will appeal more to the higher population areas? Make at least one
    plot to support your answer.

```{r aubrey1}
summary(hiphop1$county)

album <- hiphop1 %>%
  mutate(county = cut(county, breaks = c(0,99905,331582,3053793), labels=c('Small', 'Medium', 'Large'))) %>%
  filter(word == c('boo','hella')) %>%
  group_by(word, county) %>%
  summarize(pop_appeal = sum(fam1)) %>%
  drop_na()

album %>%
  ggplot(aes(x=pop_appeal, y=county, fill=word)) + 
  geom_col(position = 'dodge') +
  labs(title = "Relationship Between Word, Appeal and County Size")

```

Aubrey should pick 'Hella Bling' as his album title considering this dataset because the word 'Hella' has a greater appeal than 'Boo' in larger counties. However, since the words 'Bling' and 'Hotline' are not in the dataset more investigation is needed to be conducted!

3.  Aubrey's true life dream is to collaborate with his fellow Canadian
    musician Justin Bieber. Luckily, he knows that Bieber himself was
    one of the subjects in this study! You know that Bieber is a white
    male, aged 17-23 at the time of the study, from a relatively small
    town (10,000-60,000 people) in Ontario.

    Determine which subject is secretly Bieber, and justify your answer.

```{r aubrey2}
hiphop1 %>%
  filter(sex == 'Male', ethnicity == 'white', (age >= 17 & age <= 23), (city>=10000 & city <= 60000)) %>% 
  arrange(desc(bieber)) %>%
  filter(bieber > 4)%>%
  filter(pop >= 3 )%>%
  head(1)
```

P17 is most likely to be Justin Bieber, since p17 is the only white male of ages 17 to 23 that is from a small town with a population of around 10000 to 60000 people. Moreover, P17 knows the most Bieber songs (5) and also has a relatively high liking to pop music (3) when compared to the rest of the dataset. 


